An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-09-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of edits

rf.tt$npeak <- "RandomForest"

@@

result.container$npeak <- c("5*", "5-3-1*", "5*", "5-3-1*")
result.container$Metric <- c("cmps.max", "cmps.max", "cmps.maxbar", "cmps.maxbar")
result.container$study <- "Hamby 252"

@@

```{r param_seg_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
p.seg_plot 
```

```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
p.npeak_plot
```

\wj{new added the following}

For both Hamby set 252 and 44, we investigated the effects of different sets of parameters.
More specifically, we fixed the parameter `npeaks.set` that controls the number of peaks at each segment level to be `npeaks.set = c(5,3,1)` and modified the parameter `seg_length` that controls the length of a basis segment. 
As shown in \autoref{fig:param_seg_plot}, the default values of `seg_length` that we used for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics we are using, when `npeaks.set = c(5,3,1)`. 
However, better choices also exist.
For example, \autoref{fig:param_seg_plot} suggests that basis segment length of 75 might be a better choice than the default value for Hamby 252; basis segment length of 122 result in a higher value of sum of squares ratio for Hamby 44.

Additionally, we fixed `seg_length` to be the default values and examined different choices of `npeaks.set`.
As shown in \autoref{fig:param_npeak_plot}, `npeaks.set = c(5,3,1)`, the default value of `npeaks.set` leads to promising results in terms of the sum of squares ratio; however, other choices of `npeaks.set` could result in higher value of the sum of squares ratio.

>>>>

rf.tt$npeak <- "RF score (Hare et al)"

@@

result.container$npeak <- c("5*", "5-3-1*", "5* (Chen et al)", "5-3-1* (Chen et al)")
result.container$Metric <- c("cmps.max", "cmps.max", "cmps.maxbar", "cmps.maxbar")
result.container$study <- "Hamby 252"

@@

```{r param_seg_plot, echo=FALSE, out.width="400px", fig.cap="Comparison of results from the CMPS algorithm based on different basis segment lengths (parameter \\texttt{seg\\_length}). Only the $\\mathrm{CMPS_{max}}$ metric suggests that the default values for the basis segment length result in the best separation. Better separation is achieved based on the modified CMPS metrics, inclusing the newly suggested ones. For Hamby 252 these metrics agree that a segment length of 75 and a segment length of 122 for Hamby 44 yield better results", fig.height=3, warning = FALSE}
p.seg_plot 
```

```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3, warning = FALSE}
p.npeak_plot
```

We investigated the effects of different sets of parameters at the example of both Hamby sets 252 and 44.
More specifically, we investigated the separation achieved using the CMPS implementation under various segment lengths (controlled by the parameter   `seg_length`). Specifically, we fixed the parameter `npeaks.set` that controls the number of peaks at each segment level to be `npeaks.set = c(5,3,1)` and modified the parameter `seg_length`. 
\autoref{fig:param_seg_plot} shows that the default values of `seg_length`  for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics are used for an evaluation. 
However, we also see, that for Hamby set 252 a basis segment length of 75 is a better choice than the default segment length; a basis segment length of 122 results in a higher value of sum of squares ratio for Hamby 44.

\hh{edits up to here}
Additionally, we fixed `seg_length` to be the default values and examined different choices of `npeaks.set`.
As shown in \autoref{fig:param_npeak_plot}, `npeaks.set = c(5,3,1)`, the default value of `npeaks.set` leads to promising results in terms of the sum of squares ratio; however, other choices of `npeaks.set` could result in higher value of the sum of squares ratio.
